\documentclass[11pt,sans,a4paper]{moderncv}

\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[utf8]{inputenc}
\usepackage[left=0.5cm,top=0.5cm,right=0.5cm,bottom=0,nohead,nofoot]{geometry}
\usepackage[none]{hyphenat}
\setlength{\hintscolumnwidth}{3cm}           % if you want to change the width of the column with the dates

\name{Boris}{SABATIER}
\title{DevOps engineer}
\address{21 rue neyret}{69001 Lyon, France}
\phone[mobile]{+336 50 82 32 97}
\email{boris-cv@sabatier.io}
\extrainfo{Driving licence since 2006}

\begin{document}
	\maketitle
	\section{Employement history}
		\cventry{Since January 2015}{Computer sciences engineer}{Qualistream}{Lyon}{France}{
			\begin{itemize}
                \item Reverse-ingenering of SCCP/Skinny protocol
                \item Phone's and computeur's simulations tools improvement
                \item Managing the production environment and client issues
                \item 3D printers' assembly, calibration and maintenance
                \item Mecanical and electronical design and production of simulation's robot
			\end{itemize}
			Technologies : C, Yocto/Open embedded, Shell, Nodejs, XMLRPC,  Python, Ruby, SQL
		}
		\cventry{January 2013 \\ January 2015}{Computer sciences engineer}{Newbiz conseil}{Lyon}{France}{
			\begin{itemize}
				\item Interactive voice response development for Prosodie.
			\end{itemize}
			Technologies : C, Shell, Python, XML, XSL, VXML
		}
		\cventry{Since September 2012}{Embedded computer sciences engineer}{ADENEO}{Saint Priest}{France}{
			\begin{itemize}
				\item Embedded software development for VOLVO.
			\end{itemize}
			Technologies : C, XLM, XSL, CANalyser, VECTOR tools
		}
		\cventry{September 2009\\to September 2012}{Computer sciences engineer in sandwich course}{Electricité De France}{Villeurbanne}{France}{
			\begin{itemize}
				\item Integration of a supervisor in a scientic applications linker tool.
				\item Improvement of scientic applications linker tool.
				\item Application packaging for GNU/Debian.	
				\item Development of a contact management tool.
			\end{itemize}
			Technologies : Python, Ruby, HTML, XML, XSL, GNU/Linux, computing cluster, scientific computing, C, Shell
		}
%		\cventry{July 2012\\to August 2012}{Programmer web}{Australian Fuel Cells}{Gold-Coast}{Australia}{
%			\begin{itemize}
%				\item Enterprise website creation and Information system audit.
%			\end{itemize}
%			Technologies : HTML, JavaScript
%		}
%		\cventry{September 2008\\to August 2009}{Analyst-programmer}{Logica}{Lyon}{France}{
%			\begin{itemize}
%				\item Technical analysis of the errors happening in the information system of the Groupama insurance company.
%			\end{itemize}
%			Technologies : PacBase, MVS, JCL, DB2, COBOL
%		}
%		\cventry{January 2008\\to June 2008}{Web programmer}{AU-PC Informatique}{Montréal}{Canada}{
%			\begin{itemize}
%				\item Various web development, calendar, bug tracker ...
%			\end{itemize}
%			Technologies : PHP, HTML, JavaScript, CakePHP, apache
%		}
		\cventry{Since September 2006}{Embedded programmer}{Clubelek}{Lyon}{France}{
			Member of the INSA robotique club for participing to the French and European cup.
			\begin{itemize}
				\item Development of sensors and actuators over a CAN bus.
				\item Development of an embedded HMI and A.I..
			\end{itemize}
			Technologies : Assembly language, C, $\mu$C/OS II, CAN, SPI, USART, PIC18F, M32, STM32
		}
	\section{Education}
		\cventry{2009-2012}{Master of engineering in computer sciences and communication networks}{Lyon School of Chemistry, Physics and Electronics (CPE Lyon)}{Lyon}{France}{Embedded computing speciality}
		\cventry{2006-2008}{Two year degree in computer sciences}{Université de Lyon and the General and Vocational College of Rosemont}{Lyon and Montréal}{France and Canada}{}
		\cventry{2005-2006}{High School Diploma with advanced placement courses in chemistry, physics, mathematics, mechanics and electronics}{passed with honors}{Lyon}{France}{}
	\section{Skills}
		\subsection{Computer sciences skills}
			\cvcomputer{Language}{C, C++, Ruby, Python, SQL, XML, XSL, PHP, HTML, JS, Shell, \LaTeX, Java}{Operating System}{GNU/Linux, Mac OS X, $\mu$C/OS II, Windows}
			\cvcomputer{Microcontroleur}{PIC18F, M32, STM32}{Network}{TCP/IP, CAN, SPI, USART, SIP, SCCP, ICMP, RTP}
			\cvcomputer{Software engineering}{Merise, UML}{Project management}{V-Model, AGILE}
		\subsection{Foreign languages}
			\cvlanguage{French}{Mother tongue}{}
			\cvlanguage{English}{Read, speak, write}{CECR B2 level}
			\cvlanguage{Spanish}{Basics}{}
	\section{Leisures activites}
		\cvline{Sports}{Circus, swimming, inline skating, skiing, diving and surfing.}
		\cvline{Arts}{Circus and theater.}
\end{document}
